Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-09-28 Ben_Manuscripts/structure_paper/Draft.tex
Revisions
revisions

  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.pdf}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{columns.pdf}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.pdf}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
	exhibits wedge-like character. (d) Monomers stack on top of each other to
	create columns with short range order then assemble into pores with  
	hydrophilic head groups (blue) facing towards the pore center. (e) The 
	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
  \end{figure}

@@

  In order to more clearly identify the structural reasons for R-spots, we
  equilibrated an ordered basin sandwiched configuration at 280 K to moderately
  increase the order and therefore intensity.  Many force fields do not obtain
  the correct equilibrium structure at precisely the experimental temperature.
  Wang et al. highlighted the shortcoming of some of the most popular protein
  force field in predicting the temperature dependence of protein structural
  ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
  our membrane system, simulated at 300 K, is under-structured in the tail region
  compared to the experimental structure at 300 K. We found that lowering the
  temperature indeed better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
  suggesting that our `effective' temperature might indeed be too high,
  understabilizing structure.

  The evidence from simulations strongly suggest that the source of
  the R-spots reflection is packing of the tails in a hexagonal array.
  First, we demonstrate R-spots comes primarily from the tails, by
  removing all non-tail atoms from the trajectory and simulating the
  XRD diffraction pattern with the remaining atoms, which preserves
  R-spots (Figure~\ref{fig:tails_rzplot}).  Next, we plotted the center
  of masses of the first four tail atoms of all tails (Figure
  \ref{fig:centroids}). We measured the angle between each COM
  and its nearest neighbor COMs with respect to the
  $xy$ plane of the membrane. We see distinct peaks in the
  distribution of these angles located ca. $-60\degree$, $0\degree$,
  and $60\degree$, which is consistent with a hexagonally-packed
  configuration (Figure~\ref{fig:layered_tails}).  This ordering is
  primarily in the parts of the tail proximal to the heads, and dies
  off at the tail ends, where there is more space to fill causing them
  to pack nearly isotropically. See Section~S-\ref{S-section:tail_packing} 
  of the Supporting Information for
  a more detailed explanation of the calculation and packing
  distributions generated from different sections of the tails.

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.32\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.pdf}
  	\caption{}\label{fig:sandwiched280K}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \includegraphics[width=\textwidth]{tilt_dist.pdf}
    \caption{}\label{fig:tilt}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
	\centering
	\includegraphics[width=\textwidth]{tails_rzplot_jet.pdf}
	\caption{}\label{fig:tails_rzplot}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
    \centering
	\includegraphics[scale=0.2]{centroids.pdf}
  \caption{}\label{fig:centroids}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
        \centering
	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.pdf}
	        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
        	\centering
	        \includegraphics[width=\linewidth]{hexagonal_ft.pdf}  % generated from hexagonal_packing.py
	        \caption{}~\label{fig:hexagonal_ft}
  \end{subfigure}
  \caption{(a) R-spots increases in intensity when the temperature of the system is 
      lowered to 280K. (b) We measured the average angle made between each monomer 
      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
      near -2\degree~which is far from the 37\degree~tilt angle previously used to
      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
      from the trajectory except for carbon atoms that constitute the tails. The
      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
      Since the tails stay relatively flat, we plotted the center of mass of the first
      four carbon atoms of each tail originating from the head groups (for example,
      green colored centroids in the plot surround the red centroid in hexagonal fashion).
      Visually, the packing looks hexagonal. (e) We hypothesize
      that R-spots is the result of ordered tail packing. Defining
      the membrane plane to be 0\degree, we measured the angles between each center of 
      mass and its nearest neighbor center of masses for the equilibrated 
      sandwiched configuration simulated at 280K. Peaks appear in the distribution at 
      $-60\degree$, $0\degree$ and $60\degree$. (f) The Fourier transform of a hexagonally
      packed grid of points defined by the angles in (e) shows intensity at the same
      locations where we expect to see R-spots, as well as intensity along the $q_z$ axis
      where R-$\pi$ would appear.}~\label{fig:tail_packing}
  \end{figure}

@@

  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment because
  monomers in the simulated system stack further apart than those in the experimental
  system (Table~\ref{table:correlation_length}). We calculated $z$-direction pair distribution
  functions, $g(z)$, as described in Section~\ref{section:correlation_length}.
  %BJC11: Below is in methods but might be worth restating here? 
  %MRS12: no, OK here.
%  based on the center of mass of each monomer head group. In order
%  to calculate $g(z)$, we averaged all $z$-slices of the 3D pair distribution function, $g(x, y, z)$, 
%  (Equation~\ref{eqn:correlation}) within
%  2.1 \AA~of $g(0, 0, z)$. In this way we are measuring correlation between head 
%  groups within the same column. 
  The resulting distributions are generally characterized by decaying
  oscillatory behavior where the average distance between peaks corresponds to
  the average distance between stacked monomer head groups
  (Figure~\ref{fig:correlation}).  We calculated this equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, between monomers using
  Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked monomers is
  greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
  basins at the high end of that range.% and are on average 0.2 and 0.3 \AA~more distant.
  This behavior is not surprising since GAFF models atoms as point charges and
  does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
  it more energetically favorable for the monomers to stack closer together ~\cite{wang_development_2004}.
  It is also possible that the tails prevent close stacking of monomer head groups
  and we do not achieve the timescales necessary for them to rearrange into a
  necessarily more tightly packed configuration. We equilibrated the
  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
  into a more tightly packed configuration. Before annealing and in order to
  stabilize the hexagonal phase at 500 K, we placed harmonic restraints with 
  force constants of 1000 $kJ\ mol^{-1}\ nm^{-2}$ between head group COMs
  within each column as well as between head group COMs in
  adjacent columns. We saw no improvement in packing distance over our 300 K
  models (see further discussion in Section~\ref{section:slow_dynamics}).

  The system size, in the $z$-direction, does not significantly alter $g(z)$.
  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
  system may be necessary to fully capture the correlation function. We therefore
  equilibrated a sandwiched system with twice as many monomers per column so that
  the system size doubled in the $z$-direction. The correlation length increases
  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
  correlation functions are nearly identical and oscillatory behavior persists
  throughout $g(z)$ in both cases (See
  Figure~S-\ref{S-fig:z_correlation_overlay}).

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
  \midrule
  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
  Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
  \bottomrule
  \end{tabular}
  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
  \label{table:correlation_length}
  \end{table}

@@

  % produce figures with: structure_factor.py --random_columns -nframes 1000 --hexagonal -g 86 86 256 -thermal_disorder 2.30 0.43 1.48 -dbwl 4.4 --pore_radius 6.6 -box 85 85 352 -sr 0
  % Adjust sr from 0 to .75 to 1
  \begin{figure}
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr0.pdf}
  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr75.pdf}
  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr100.pdf}
  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
  \end{subfigure}
  \caption{As we increase column independence using the $f$ parameter, the
	  intensity of R-$\pi$ decreases and the $q_r$ cross-section of the simulated
	  diffraction pattern becomes more smooth.  (a) When we place all columns at the
	  same reference $z$ coordinate, $f$ = 0, the intensity of R-$\pi$ is 18.3 and is
	  characterized by sharp Bragg-like peaks. (b) When columns have a moderate
	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
	  still exist. (c) When columns are completely independent, $f$ = 1, the
	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
          relatively smooth.}\label{fig:column_displacement}
  \end{figure}

  It therefore seems likely that the discrepancy between the intensity of
  R-$\pi$ generated from our simulations versus experiment is primarily due to
  highly correlated columns in our initial configurations, likely due to the
  highly symmetric starting configuration. If the columns were uncorrelated,
  $g(z)$ of the ordered sandwiched system would very closely resemble
  Figure~\ref{fig:z_correlation_sandwich} when we average all $z$-slices of the
  3D correlation function. When we include all $z$-slices in $g(z)$ for our
  system, rather than restricting it to those $z$-slices within 2.1 \AA of the
  center of the correlation function (Section~\ref{section:correlation_length}),
  the function shows oscillatory behavior and the correlation length
  nearly triples to 12.4 $\pm$ 0.7 \AA. (Figure~\ref{fig:z_correlation_fullbox}).
  Since all columns in our initial configuration are started at the same
  $z$-coordinate, $g(z)$ on average exhibits correlation of head groups with
  other head groups within the same column, with head groups in other columns
  within the same pore, and with head groups in different pores.

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
	  we double the disorder (Noise factor = 2), the FWHM decreases by
	  51\%.}\label{fig:qy_fwhm}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.pdf}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.pdf}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.pdf}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}

@@

  We can explain the discrepancies between R-$\pi$ seen experimentally
  and in simulation using what we have shown in this section. The stacking
  distance between monomer head groups is too large, likely due to failures
  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
  ordering in the $z$-direction in addition to high degrees of correlation 
  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
  which is also likely a consequence of columns that are too highly correlated.
  If we limit ourselves to standard simulation techniques, it is necessary to 
  average data generated from ensembles of independent simulation trajectories
  in order to begin converging on time-averaged descriptions of the system's
  molecular structure.

  A secondary conclusion drawn from the evidence in this section is 
  that the architecture of each column is likely in between our sandwiched
  and parallel displaced configurations. The parallel displaced configuration 
  that we have simulated in this paper is an exaggerated manifestation of the 
  parallel displaced $\pi-\pi$ stacking mode. Not only is the intensity of R-$\pi$
  calculated from the ensemble of parallel displaced simulations in close agreement
  with experiment, but the experimental WAXS pattern shows faint off-axis features
  at the same $q_r$ value as R-double which are only present in simulated patterns
  generated from parallel displaced configurations. The monomers may prefer to be
  parallel displaced, but their displacement is likely only slightly shifted, on 
  the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
  (see Figure~S-\ref{S-fig:between_pd} of the Supporting Information). In this way,
  columns can more easily act 
  independently while maintaining some features of parallel displaced structure.

@@

  The appearance of R-double implies a vertical modulation in electron density
  every 7.4 \AA. We are not able to achieve such modulation using our simple
  initial configurations. Although the position of monomers in parallel displaced
  configurations alternate every other layer, such a configuration will not
  produce R-double, but only off-axis reflections at the same $q_z$
  value~\cite{harburn_atlas_1975}. There is not a unique solution that describes
  the origin of R-double. Extracting the exact relationship between a diffraction
  pattern and its real space configuration is well-known as the phase
  problem~\cite{taylor_phase_2003}. We have proposed configurations that
  result in the appearance of R-double below, and we can speculate which makes
  the most physical sense. It appears that we cannot achieve a long-term stable
  system that exhibits R-double without the inclusion of small amounts of water
  in the pores.

@@

  Of all the configurations tested, it is most likely that R-double is induced
  by water molecules as described above since it is the only mechanism that can
  be observed without position restraints. The extent of the hydrogen-bonded
  network that forms is largely determined by the accuracy of the forcefield. It
  is possible that a more realistic force field would make the effect stronger or
  weaker. If this is truly the mechanism, it implies that the system studied by
  Feng et al.\cite{feng_scalable_2014,feng_thin_2016} was not truly a
  thermotropic Col\textsubscript{h} phase. Rather, they were very low water
  content H\textsubscript{II} phases unintentionally created due to the neat
  monomers' hydroscopicity.  Anecdotal evidence from other researchers suggests
  that membranes are less likely to assemble under completely dry
  conditions, supporting the idea %~\cite{personal_communication_with_mike_mcgrath} <- BJC16: what do I do with this?
  that the ``dry'' structures do absorb some water. This detail may therefore be
  important for reproducing the results of Feng et al.

>>>>

  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.pdf}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.pdf}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{columns.pdf}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.pdf}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
	exhibits wedge-like character. (d) Monomers stack on top of each other to
	create columns with short range order then assemble into pores with  
	hydrophilic head groups (blue) facing towards the pore center. (e) The 
	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
  \end{figure}

@@

  In order to more clearly identify the structural reasons for R-spots, we
  equilibrated an ordered basin sandwiched configuration at 280 K to moderately
  increase the order and therefore intensity. Many force fields do not obtain
  the correct equilibrium structure at precisely the experimental temperature.
  Wang et al. highlighted the shortcoming of some of the most popular protein
  force fields in predicting the temperature dependence of protein structural
  ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
  our membrane system, simulated at 300 K, is under-structured in the tail region
  compared to the experimental structure at 300 K. We found that lowering the
  temperature better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
  suggesting that our `effective' temperature might indeed be too high,
  understabilizing structure.

  The evidence from simulations strongly suggest that the source of
  the R-spots reflection is packing of the tails in a hexagonal array.
  First, we demonstrated that R-spots comes primarily from the tails by
  removing all non-tail atoms from the trajectory and simulating the
  XRD pattern with the remaining atoms, which preserves
  R-spots (Figure~\ref{fig:tails_rzplot}). Next, we plotted the center
  of masses of the first four tail atoms of all tails (Figure
  \ref{fig:centroids}). We measured the angle between each COM
  and its nearest neighbor COMs with respect to the
  $xy$ plane of the membrane. We see distinct peaks in the
  distribution of these angles located ca. $-60\degree$, $0\degree$,
  and $60\degree$, which is consistent with a hexagonally-packed
  configuration (Figure~\ref{fig:layered_tails}).  This ordering is
  primarily in the parts of the tail proximal to the heads, and dies
  off at the tail ends, where there is more space to fill causing them
  to pack nearly isotropically. See Section~S-\ref{S-section:tail_packing} 
  of the Supporting Information for
  a more detailed explanation of the calculation and packing
  distributions generated from different sections of the tails.

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.32\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.pdf}
  	\caption{}\label{fig:sandwiched280K}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \includegraphics[width=\textwidth]{tilt_dist.pdf}
    \caption{}\label{fig:tilt}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
	\centering
	\includegraphics[width=\textwidth]{tails_rzplot_jet.pdf}
	\caption{}\label{fig:tails_rzplot}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
    \centering
	\includegraphics[scale=0.2]{centroids.pdf}
  \caption{}\label{fig:centroids}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
        \centering
	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.pdf}
	        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
        	\centering
	        \includegraphics[width=\linewidth]{hexagonal_ft.pdf}  % generated from hexagonal_packing.py
	        \caption{}~\label{fig:hexagonal_ft}
  \end{subfigure}
  \caption{(a) R-spots increases in intensity when the temperature of the system is 
      lowered to 280K. (b) We measured the average angle made between each monomer 
      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
      near -2\degree~which is far from the 37\degree~tilt angle previously used to
      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
      from the trajectory except for carbon atoms that constitute the tails. The
      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
      Since the tails stay relatively flat, we plotted the COM of the first
      four carbon atoms of each tail originating from the head groups (for example,
      green colored COMs in the plot surround the red COM in hexagonal fashion).
      Visually, the packing looks hexagonal. (e) We hypothesize
      that R-spots is the result of ordered tail packing. Defining
      the membrane plane to be 0\degree, we measured the angles between each center of 
      mass and its nearest neighbor center of masses for the equilibrated 
      sandwiched configuration simulated at 280 K. Peaks appear in the distribution at 
      $-60\degree$, $0\degree$ and $60\degree$. (f) The Fourier transform of a hexagonally
      packed grid of points defined by the angles in (e) shows intensity at the same
      locations where we expect to see R-spots, as well as intensity along the $q_z$ axis
      where R-$\pi$ would appear.}~\label{fig:tail_packing}
  \end{figure}

@@

  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment because
  monomers in the simulated system stack further apart than those in the experimental
  system (Table~\ref{table:correlation_length}). We calculated $z$-direction pair distribution
  functions, $g(z)$, as described in Section~\ref{section:correlation_length}.
  %BJC11: Below is in methods but might be worth restating here? 
  %MRS12: no, OK here.
%  based on the center of mass of each monomer head group. In order
%  to calculate $g(z)$, we averaged all $z$-slices of the 3D pair distribution function, $g(x, y, z)$, 
%  (Equation~\ref{eqn:correlation}) within
%  2.1 \AA~of $g(0, 0, z)$. In this way we are measuring correlation between head 
%  groups within the same column. 
  The resulting distributions are generally characterized by decaying
  oscillatory behavior where the average distance between peaks corresponds to
  the average distance between stacked monomer head groups
  (Figure~\ref{fig:correlation}).  We calculated this equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, between monomers using
  Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked monomers is
  greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
  basins at the high end of that range.% and are on average 0.2 and 0.3 \AA~more distant.
  This behavior is not surprising since GAFF models atoms as point charges and
  does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
  it more energetically favorable for the monomers to stack closer together~\cite{wang_development_2004}.
  It is also possible that the tails prevent close stacking of monomer head groups
  and we do not achieve the timescales necessary for them to rearrange into a
  necessarily more tightly packed configuration. We equilibrated the
  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
  into a more tightly packed configuration. Before annealing and in order to
  stabilize the hexagonal phase at 500 K, we placed harmonic restraints with 
  force constants of 1000 $kJ\ mol^{-1}\ nm^{-2}$ between head group COMs
  within each column as well as between head group COMs in
  adjacent columns. We saw no improvement in packing distance over our 300 K
  models (see further discussion in Section~\ref{section:slow_dynamics}).

  The system size, in the $z$-direction, does not significantly alter $g(z)$.
  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
  system may be necessary to fully capture the correlation function. We therefore
  equilibrated a sandwiched system with twice as many monomers per column so that
  the system size doubled in the $z$-direction. The correlation length increases
  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
  correlation functions are nearly identical and oscillatory behavior persists
  throughout $g(z)$ in both cases (See
  Figure~S-\ref{S-fig:z_correlation_overlay} in the Supporting Information).

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
  \midrule
  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
  Experiment         & --                 &    3.70                    & 9 $\pm$ 1               \\
  \bottomrule
  \end{tabular}
  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
  \label{table:correlation_length}
  \end{table}

@@

  % produce figures with: structure_factor.py --random_columns -nframes 1000 --hexagonal -g 86 86 256 -thermal_disorder 2.30 0.43 1.48 -dbwl 4.4 --pore_radius 6.6 -box 85 85 352 -sr 0
  % Adjust sr from 0 to .75 to 1
  \begin{figure}
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr0.pdf}
  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr75.pdf}
  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr100.pdf}
  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
  \end{subfigure}
  \caption{As we increase column independence using the $f$ parameter, the
	  intensity of R-$\pi$ decreases and the $q_r$ cross-section of the simulated
	  diffraction pattern becomes more smooth.  (a) When we place all columns at the
	  same reference $z$ coordinate, $f$ = 0, the intensity of R-$\pi$ is 18.3 and is
	  characterized by sharp Bragg-like peaks. (b) When columns have a moderate
	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
	  to 3.2. The edges of the peak are beginning to smooth out, but sharp peaks
	  still exist. (c) When columns are completely independent, $f$ = 1, the
	  intensity of R-$\pi$ decreases 8-fold to 2.1 and the cross-section is
          relatively smooth.}\label{fig:column_displacement}
  \end{figure}

  It therefore seems likely that the discrepancy between the intensity of
  R-$\pi$ generated from our simulations versus experiment is primarily due to
  highly correlated columns in our initial configurations, likely due to the
  highly symmetric starting configuration. If the columns were uncorrelated,
  $g(z)$ of the ordered sandwiched system would very closely resemble
  Figure~\ref{fig:z_correlation_sandwich} when we average all $z$-slices of the
  3D correlation function. When we include all $z$-slices in $g(z)$ for our
  system, rather than restricting it to those $z$-slices within 2.1 \AA~of the
  center of the correlation function (Section~\ref{section:correlation_length}),
  the function shows oscillatory behavior and the correlation length
  nearly triples to 12.4 $\pm$ 0.7 \AA~(Figure~\ref{fig:z_correlation_fullbox}).
  Since all columns in our initial configuration are started at the same
  $z$-coordinate, $g(z)$ on average exhibits correlation of head groups with
  other head groups within the same column, with head groups in other columns
  within the same pore, and with head groups in different pores.

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
	  FWHM of the $q_r$ cross-section of R-$\pi$. When we cut the amount of $r$ and
	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
	  we double the disorder (Noise factor = 2), the FWHM decreases by
	  51\%.}\label{fig:qy_fwhm}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.pdf}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.pdf}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.pdf}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main (400 ns) ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms, as a function of distance from the pore center,
  calculated from the first 5 ns of the main system simulation trajectory (black lines) 
  and from the ensemble of trajectories (purple) look qualitatively similar. The 95 \%
  confidence interval generated based on the ensemble of simulations is shaded in purple.}\label{fig:ensemble_stds}
  \end{figure}

@@

  We can explain the discrepancies between R-$\pi$ seen experimentally
  and in simulation using what we have shown in this section. The stacking
  distance between monomer head groups is too large, likely due to failures
  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
  ordering in the $z$-direction in addition to a high degree of correlation 
  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
  which is also likely a consequence of columns that are too highly correlated.
  If we limit ourselves to standard simulation techniques, it is necessary to 
  average data generated from ensembles of independent simulation trajectories
  in order to begin converging on time-averaged descriptions of the system's
  molecular structure.

  A secondary conclusion drawn from the evidence in this section is 
  that the architecture of each column is likely in between our sandwiched
  and parallel displaced configurations. The parallel displaced configuration 
  that we have simulated in this paper is an exaggerated manifestation of the 
  parallel displaced $\pi-\pi$ stacking mode. Not only is the intensity of R-$\pi$
  calculated from the ensemble of parallel displaced simulations in close agreement
  with experiment, but the experimental WAXS pattern shows faint off-axis features
  at the same $q_r$ value as R-double which are only present in simulated patterns
  generated from parallel displaced configurations. The monomers may prefer to be
  parallel displaced, but their displacement is likely only slightly shifted, on 
  the $xy$ plane, from the COM of their vertically adjacent neighbors 
  (see Figure~S-\ref{S-fig:between_pd} of the Supporting Information). In this way,
  columns can more easily act 
  independently while maintaining some features of parallel displaced structure.

@@

  The appearance of R-double implies a vertical modulation in electron density
  every 7.4 \AA. We are not able to achieve such modulation using our simple
  initial configurations. Although the position of monomers in parallel displaced
  configurations alternate every other layer, such a configuration will not
  produce R-double, but only off-axis reflections at the same $q_z$
  value~\cite{harburn_atlas_1975}. There is not a unique solution that describes
  the origin of R-double. Extracting the exact relationship between a diffraction
  pattern and its real space configuration is well-known as the phase
  problem~\cite{taylor_phase_2003}. We have proposed configurations that
  result in the appearance of R-double below, and we can speculate which makes
  the most physical sense.

% Following is in previous paragraph
%It appears that we cannot achieve a long-term stable
%  system that exhibits R-double without the inclusion of small amounts of water
%  in the pores.

@@

  Of all the configurations tested, it is most likely that R-double is induced
  by water molecules as described above since it is the only mechanism that can
  be observed without position restraints. The extent of the hydrogen-bonded
  network that forms is largely determined by the accuracy of the forcefield. It
  is possible that a more realistic force field would make the effect stronger or
  weaker. If this is truly the mechanism, it implies that the system studied by
  Feng et al.\cite{feng_scalable_2014,feng_thin_2016} was not truly a
  thermotropic Col\textsubscript{h} phase. Rather, they were very low water
  content H\textsubscript{II} phases unintentionally created due to the neat
  monomers' hydroscopicity. Anecdotal evidence from other researchers suggests
  that these membranes are less likely to assemble under completely dry
  conditions, supporting the idea %~\cite{personal_communication_with_mike_mcgrath} <- BJC16: what do I do with this?
  that the ``dry'' structures do absorb some water. This detail may therefore be
  important for reproducing the results of Feng et al.
